Subjective Experience of Demands and Resources across O*NET Job Elements

### 2024-01-04 Submission.Rmd
updating figure references
reworking intro

abstract: |
  Much of our understanding of job demands and resources rests on an assumption that some aspects of jobs are resources and some are demands. Our primary aim was to document the degree of variability in subjective ratings of job characteristics with respect to interpretation as resource and demand. Secondarily, we quantify the degree to which perceptions match the literature-implicated resources/demands of job characteristics. O*NET work characteristics were rated by 568 employed respondents. Job characteristics were not commonly categorized as solely resource or demand. Rather, job resources were also frequently viewed as challenging demands. These findings have implications for job design and administration - resource-laden elements may also be interpreted by workers as demands.

@@

csl               : "apa7.csl"
#documentclass     : "apa7" #interact
classoption       : "man"
#output            : "word_document"
output            : papaja::apa6_pdf

@@

Research on the job demands-resources model [@demerouti2001job] and later job demands-resources theory [@bakker2017job] highlights the importance of work characteristics on the experience of motivation and strain, which subsequently have an impact on job performance, among other outcomes. However, much of our existing knowledge regarding the way this model functions is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands. We build on the work of a small, but growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges]. We extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resources) in the workplace, with a primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics. Prior to presenting the current study in detail, we provide a brief overview of the relevant theories and relevant empirical work on this topic.

@@

The overarching context for this study is that of the job demands-resources theory, which is an expansion of the well-studied job demands-resources model [@demerouti2001job]. One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics via job resources and demands. *Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job]. In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; @demerouti2001job). The perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; @bakker2014job). Of particular importance here is that it is *the perception* of a characteristic or situation that determines which process an employee will experience despite the *a priori* objective assumption of a characteristic as objectively a "demand" or "resource". We explore this further below.

@@

Although much of our research on job demands in particular is based on *a priori* classifications [@searle2015merits], the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand). The stress process speaks to how such individual difference in appraisal is possible. @lazarus1984stress presented the transactional theory of stress and coping, which states that people cognitively appraise stimuli in their environments on a continuous basis. Via this process, meaning is assigned to stimuli based on potential for gain or loss. If appraised as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping. The cycle of appraisal then continues based on the action to cope with the stressor [@lazarus1984stress]. Coping is considered a secondary appraisal and is the way that someone chooses to manage a stressor. Although not suggested by the names, primary and secondary appraisals can happen simultaneously. For instance, available resources to cope with a stressor may influence an employee’s initial appraisal of a stressor (e.g., amount of time [resource] available to prepare for the speech may influence one’s primary appraisal of this task).

@@

Although there is a tendency to attach a negative connotation to the word “stress”, @selye1936syndrome defined stress as simple a response to change. We return to the public figure for this next section. Consider two employees be called upon to serve as spokespeople for their organization. One may appraise the circumstance as an opportunity to positively influence others, while the other may feel daunted by the task.

The challenge-hindrance stressor framework suggests that the way we understand reactions to stressors requires consideration of how people feel about a given stressor [@cavanaugh2000empirical], in line with @lazarus1984stress. @cavanaugh2000empirical delineated between two forms of demands – that of *challenge* and *hindrance* demands. Challenge demands promote mastery, personal growth, and future gains – these stressors should lead to coping strategies that facilitate achievement. Stressors like time pressure and responsibility are considered challenge stressors/demands. Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Hindrance stressors (e.g., role conflict, role ambiguity, politics) are associated with negative job behaviors and attitudes. This distinction between challenges and hindrances has been of value in determining which demands are related to various outcomes. The original work on this topic suggests that challenge stressors are typically associated with positive outcomes and hindrance stressors are associated with negative outcomes [e.g., @cavanaugh2000empirical].

```{r reproduced, echo=FALSE, fig.cap="LePine's (2022) revised challenge-hindrance stressor framework."}
library(magick)
library(grid)

@@

Prior to considering the subsequent empirical work on this topic, it is of value to explore *why* different outcomes are expected with these forms of demands. @lepine2022challenge explain the mechanisms by which demands are related to performance and wellbeing outcomes. Similar to the job-demands resources theory [@bakker2017job], challenge and hindrance demands elicit two different paths or processes. First, challenge stressors typically result in a challenge appraisal, and engagement is likely to happen as a result. Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing. Of note is that this energy may be depleted eventually, leading to strain. Hindrance stressors elicit a different process. Disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing. This happens because resources are depleted via frustrations and other affectively negative reactions [@lepine2022challenge]. The theoretical associations that drive the current study's purpose are presented in Figure \@ref(fig:reproduced), which has been reproduced from @lepine2022challenge.

@@

The integration of the literature above culminates with two primary hypotheses. The first addresses whether employees generally agree on their appraisals of job characteristics as resources or challenge or hindrance demands. For instance, although challenge stressors tend to be appraised more so as challenges, and hindrance stressors tend to be appraised more as hindrances than challenges, others have reported variability in these appraisals [e.g., @lepine2022challenge]. @lepine2022challenge, in fact, argues that the challenge-hindrance stressor framework acknowledges that these appraisals are not universal. Thus, it is quite possible, given the theoretical and empirical evidence presented above, that there is wide variability in individual appraisal of work activities and context such that some people may rate a given activity as a resource and others a hindrance.

@@

Two exploratory questions further address whether our *literature-implicated* resources (e.g., autonomy) and demands are consistently rated as our research models suggest across the job-demands resources theory [@bakker2017job] and challenge-hindrance stressor framework [@cavanaugh2000empirical].

>*Research Question 1*: Do literature-implicated resources materialize as perceived resources?

>*Research Question 2*: Do literature-implicated demands materialize as job demands?

@@

a <- ggplot(topresource, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="blue", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Most Agreed Upon as a Resource") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6))

@@

b <- ggplot(topchallenge, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="yellow", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Most Agreed Upon as a Challenge") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6))

@@

c <- ggplot(tophindrance, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="red", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Most Agreed upon as a Hindrance") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6))

@@

d <- ggplot(bottomresource, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="blue", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Least Agreed Upon as a Resource") + 
  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))

@@

e <- ggplot(bottomchallenge, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="yellow", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Least Agreed Upon as a Challenge") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))

@@

f <- ggplot(bottomhindrance, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="red", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Least Agreed upon as a Hindrance") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))

@@

The second hypothesis stated that job characteristics would not be uniquely categorized as a resource or demand. Table 1 provides the correlations among the O\*Net "scale"-level groupings across ratings of resource, challenge, and hindrance. We would expect to see minimal correlations if job characteristics *were* uniquely categorized. First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (*SD* = .13, range from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, *M* = .43, *SD* =.16). Hindrance categories, however, had less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, *M* = .62, *SD* = .17. When people perceived hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater differentiation. Taken with the Figure 3 takeaway, this hints that workers are likely either generally experiencing hindrances at work or they are not.

@@

In sum, this endeavor explored the job-demands-resources literature from a unique lens from within a universally accessible framework. We showed that there are far more individual differences in how employees perceive demands and resources than much of our current research suggests. While resources and challenges idiosyncratic more similarly experienced, what is experienced as a hindrance tends to be idiosyncratic. 
```{r}

@@

\newpage

>>>>

abstract: |
  Much of our understanding of job demands and resources rests on an assumption that some aspects of jobs are resources and some are demands. This study documents the degree of variability in subjective ratings of job characteristics with respect to interpretation as resource and demand. Next, we quantify the degree to which perceptions match the literature-implicated resources/demands of job characteristics and also document associations with stress, burnout, and engagement. Job characteristics were not commonly categorized as solely resource or demand. Rather, job resources were also frequently viewed as challenging demands. OUTCOME VARIABLE INFORMATION HERE. These findings have implications for job design and administration - resource-laden elements may also be interpreted by workers as demands.

@@

csl               : "apa7.csl"
#documentclass     : "apa7" #interact
classoption       : "jou"
#output            : "word_document"
output            : papaja::apa6_pdf

@@

Research on the job demands-resources model [@demerouti2001job] and later job demands-resources theory [@bakker2017job] highlights the importance of work characteristics on the experience of motivation and strain as well as other, more distal outcomes. However, much of our existing knowledge regarding the way these relationships function is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands. We build on the work of a small, but growing number of researchers who argue that the work elements may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges], with primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics. Prior to presenting the current study in detail, we provide a brief overview of the relevant theories and relevant empirical work on this topic.

@@

*Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job]. In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is commonly cited as a demand; @demerouti2001job). The perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; @bakker2014job). Of particular importance here is that it is *the perception* of a characteristic or situation that determines which process an employee will experience despite the *a priori* objective assumption of a characteristic as objectively a "demand" or "resource". We explore this further below.

@@

Although much of our research on job demands based on a priori classifications [@searle2015merits], the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand). @lazarus1984stress's transactional theory of stress and coping suggests that people cognitively appraise stimuli in their environments on a continual basis. If a task or situation is appraised as threatening, challenging, or possibly harmful, the resulting emotional distress initiates a coping response. These primary and secondary appraisals can happen simultaneously. For example, perceiving ample resources to cope with a stressor may influence an employee’s initial appraisal of a stressor (e.g., amount of time [resource] available to prepare for the speech may influence one’s primary appraisal of this task).

@@

Demand --> appraisal (as challenge or hindrance)

Demand=Stressor

Decision (can overcome or not )

@cavanaugh2000empirical delineated between two forms of demands -- *challenges* and *hindrances*. Both are considered stressors [e.g., @cavanaugh2000empirical]. Challenge demands promote mastery, personal growth, and future gains – these stressors should lead to coping strategies that facilitate achievement. Work characteristics consistent with this definition include time pressure and responsibility. Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Hindrance stressors in a work context include role conflict, role ambiguity, and organizational politics. The original work on this topic suggests that challenge stressors are typically associated with positive outcomes and hindrance stressors are associated with negative outcomes [e.g., @cavanaugh2000empirical].

```{r reproduced, eval=FALSE, echo=FALSE, fig.cap="Going to put in new comprehensive picture."}
library(magick)
library(grid)

@@

@lepine2022challenge explain the mechanisms by which demands are related to performance and wellbeing outcomes. First, stressors appraised as challenges typically result in a challenge appraisal, and engagement is likely to happen as a result. Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing. Of note is that this energy may be depleted eventually, leading to strain. Stressors appraised as hindrances elicit a different process. Disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing. This happens because resources are depleted via frustrations and other affectively negative reactions [@lepine2022challenge]. The theoretical associations that drive the current study's purpose are presented in Figure \@ref(fig:reproduced), which has been reproduced from @lepine2022challenge.

@@

The integration of the literature above culminates with two primary hypotheses. The first addresses whether employees generally agree on their appraisals of job characteristics as resources or challenge or hindrance demands. For instance, although challenge stressors tend to be appraised more so as challenges, and hindrance stressors tend to be appraised more as hindrances than challenges, others have reported variability in these appraisals [e.g., @lepine2022challenge]. @lepine2022challenge, in fact, argues that the challenge-hindrance stressor framework acknowledges that these appraisals are not universal. Thus, it is quite possible, given the theoretical and empirical evidence presented above, that there is wide variability in individual appraisal of work activities and context such that some people may rate a given activity as a resource and others a hindrance. COMBINE 1 and 2:

@@

>Hyp 3: Are these perceptions aligned with the literature's presentation of job characteristics?

The second set of analyses focuses on associations. Do demands and resources have implications for work outcomes?

>Hyp 4.a: Job resources are associated with greater engagement, less stress, and less burnout. 
>Hyp 4.b: More hindrances leads to less engagement, more stress, and greater burnout.

>Hyp 4.exploratory: More challenges leads to greater satisfaction, engagement, and burnout.

@@

a <- ggplot(topresource, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="blue", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Most Consensus as a Resource") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6))

@@

b <- ggplot(topchallenge, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="yellow", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Most Consensus as a Challenge") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6))

@@

c <- ggplot(tophindrance, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="red", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Most Consensus as a Hindrance") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6))

@@

d <- ggplot(bottomresource, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="blue", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Lack of Consensus as a Resource") + 
  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))

@@

e <- ggplot(bottomchallenge, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="yellow", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Lack of Consensus as a Challenge") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))

@@

f <- ggplot(bottomhindrance, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="red", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Lack of Consensus as a Hindrance") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))

@@

The second hypothesis stated that job characteristics would not be uniquely categorized as a resource or demand. Table 1 provides the correlations among the O\*Net "scale"-level groupings across ratings of resource, challenge, and hindrance. We would expect to see minimal correlations if job characteristics *were* uniquely categorized. First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (*SD* = .13, range from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, *M* = .43, *SD* =.16). Hindrance categories, however, had less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, *M* = .62, *SD* = .17. When people perceived hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater differentiation. Taken with the Figure \@ref(fig:scalelevelgraphs) takeaway, this hints that workers are likely either generally experiencing hindrances at work or they are not.

@@

In sum, this endeavor explored the job-demands-resources literature from a unique lens from within a universally accessible framework. We showed that there are far more individual differences in how employees perceive demands and resources than much of our current research suggests. While resources and challenges idiosyncratic more similarly experienced, what is experienced as a hindrance tends to be idiosyncratic.

```{r}

@@
